---
title: "Obtaining Historical Weather Data from Qld Government DES Website"
output: rmarkdown::html_vignette
bibliography: ../man/fragments/cropgrowdays.bib
vignette: >
  %\VignetteIndexEntry{Obtaining Historical Weather Data from Qld Government DES Website}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#:"
)
```

```{r child="../man/fragments/intro.Rmd"} 
```

## Obtaining Australian SILO Meteorological Data for One Site

You can use the `get_silodata` function to retrieve SILO weather data
from the Queensland Government DES longpaddock website
<https://www.longpaddock.qld.gov.au>.

The SILO (Scientific Information for Land Owners) is a database of
Australian climate data hosted by the Science and Technology Division
of the Queensland Government's Department of Environment and
Science. These datasets are constructed from Australian Bureau of
Meteorology observations and provide national coverage with
interpolated infills for missing data. Weather station data is the
observed data while the gridded data is interpolated. Typically, for
most variables, weather data can be obtained for the period 1 January
1889 to yesterday. Please see
<https://www.longpaddock.qld.gov.au/silo/about/overview/> for a more
in-depth description.

SILO products are provided free of charge to the public for use under
the Creative Commons Attribution 4.0 license. However, please note
that this is a free service and so a fair-use limit is imposed even if
exact limits are not specified.

```{r child="../man/fragments/boonah_description.Rmd"} 
```

Finally, please note that by default, the `APSIM` format is returned
and a date column called `date_met` is appended to the retrieved
data. Many other formats are available and may need to be processed
differently.

## Obtaining SILO Data for Multiple Sites

Use the `get_multi_silodata` function to get SILO data for multiple
sites. This is a simple wrapper to `get_silodata`. The main
differences are that `latitude` and `longitude` are numerical vectors
and the new parameter `Sitename`is a character vector of site names or
site labels.


A simple example is:
```{r get-data2, eval=FALSE}
two_sites  <- get_multi_silodata(latitude = c(-27.00, -28.00),
                     longitude = c(151.00, 152.00),
                     Sitename = c("Site_1", "Site_2"),
                     START = "20201101", FINISH = "20201105",
                     email = "MY_EMAIL_ADDRESS")
```

The retrieved data are:
```{r}
two_sites
```

Note that, to obtain gridded data, you need to supply at least each
site's latitude and longitude as well as your email address by
replacing `MY_EMAIL_ADDRESS` with your email address. The data is
freely available under the Creative Commons 4.0 License.

## Other Australian weather data

The excellent `R` package `bomrang` [@sparks2017; @sparks2021], which
used to provide forecast, bulletin and historic data (see
https://github.com/ropensci-archive/bomrang/), was archived after the
Australian Bureau of Meteorology appeared to ban scraping on it's
websites in March 2021. Adam Sparks and team are currently developing
an `R` package `weatherOz` which also includes a `SILO` wrapper (see
https://dpird-fsi.github.io/weatherOz/reference/get_silo.html).  Paid
services for some forecast, current and historical weather data for
areas of interest may be available but these are not discussed here.

## References
