Example `R` syntax is provided for calculating daily mean radiation,
total rainfall, growing degree dates and the number of stress days
between two dates. Alternatively, a number of days before or after a
certain date may be specified.

Note that employing mapping functions to add agrometeorological
variables to large data frames can take a substantial amount of
computational time. We describe how to employ the `furrr` package,
which provides a relatively simple way to apply mapping functions in
parallel, to speed up these calculations.

### Growing Degree Days

The `growing_degree_days` function calculates the sum of degree days
for each day $i = 1 \ldots n$. The growing degree days $GDD$ summed
over $n$ days are

$$GDD = \sum_i^n (Tmax_{i} + Tmin_{i}) / 2 - T_{base}$$ 

during specified dates for a tibble/data frame of daily weather
data. For each day $i$, the maximum temperature is $Tmax_{i}$ and
minimum is $Tmin_{i}$. Note that the maximum temperature $Tmax$ is
capped at `maxt_cap` degrees when calculating average temperature. The
defaults are $T_{base} = 5^{\circ}C$ and $Tmax$ is capped at
$Tmax_{cap} = 30^{\circ}C$. (See @mcmaster1997 or
 https://farmwest.com/transition/bcagriweather/ [@anonGDD])

The *gdd* functions in the *pollen* package [@pollen2019] and in
*agroclim* [@agroclim2020] also calculate growing degree days. While
these functions do not allow for a fixed number of days, and in the
case of *agroclim::gdd* assume a more limited growing season since the
function appears to be tailored to grapes, further variations on the
formula above as outlined in @baskerville1969 are available.

To calculate the growing degree days at Boonah using weather data from
the `boonah` object between flowering and harvest use:

```{r gdd}
## Growing Degree Days between two dates
crop$flower_date[4]     # flowering date for 4th field or farm in 'crop'
crop$harvest_date[4]    # harvest date for 4th field or farm in 'crop'
growing_degree_days(boonah, startdate = crop$flower_date[4],
                         enddate = crop$harvest_date[4]) #, monitor = TRUE)
```

### Stress days

`stress_days_over` calculates the number of days when the maximum
temperature exceeded a base line `stress_temp` during specified dates
for a tibble/data frame of daily weather data. The default
`stress_temp` is set at $30^{\circ}C$.

To calculate the number of stress days at Boonah between flowering and
harvest, use:

```{r stress_days}
## Stress days  between two dates
stress_days_over(boonah, startdate = crop$flower_date[4],
                 enddate = crop$harvest_date[4]) # , monitor = TRUE)
```

### Cumulative calculations

`cumulative` calculates the sum total of daily values between two
dates from a tibble/data frame of daily weather data. Typically this
is used for solar radiation or rainfall.

To calculate the total rainfall at Boonah between flowering and
harvest, use:

```{r cumulative}
## cumulative rainfall between two dates (flowering and harvest)
cumulative(boonah, var = rain, startdate = crop$flower_date[4],
           enddate = crop$harvest_date[4])
```

### Daily means

`daily_mean` calculates the daily average of a variable between two
dates from a tibble/data frame of daily weather data. Typically this
would be for temperature, rainfall or solar radiation.

To calculate daily mean radiation in the 3 day period from day of
flowering onwards (which also includes day of flowering), use:

```{r daily_mean}
## daily mean radiation for the three days ending on crop$flower_date[4]
crop$flower_date[4] # a particular flowering date
daily_mean(boonah, enddate = crop$flower_date[4], ndays = 3,
           monitor = TRUE)
```

## Extracting weather data from a tibble or dataframe

To extract column(s) from a tibble/data frame of daily weather data
between two specified dates we use `weather_extract`. Either specify
the start and end dates or specify one of these dates and also the
number of days after or before, respectively.

```{r weather1}
## Extract daily rainfall & maximum temperature data using %>% pipe operator
boonah |>
  weather_extract(c(rain, maxt), date = date_met, startdate = ymd("2019-08-16"),
                  enddate = ymd("2019-08-21"))
```

## Adding agrometeorological variables to dataframes

We can add agrometeorological variables to the `crop` tibble using the
`tidyverse` functions `map_dbl`, `map_dbl2` and `pmap` to calculate
new columns employing the weather data from the `boonah` object. Use
`map_dbl` for one varying date and `map_dbl2` for varying start and
end dates. For more than two varying parameters, which may be
necessary if for instance our weather object contained multiple
locations or sites, then we can use `pmap`. These functions are from
the `purrr` library. Alternatively, we could use functions from the
`apply` family such as `mapply` from the `base` package.

To add growing degree days 7 days post sowing and the number of stress
days above $30^\circ C$ from flowering to harvest to the `crop`
tibble, then we employ the following `mutate` syntax to extract the
appropriate weather data from the `boonah` weather data object.

```{r, add2crop-gdd}
## Growing degree and stress days
crop2 <- crop |>
  dplyr::mutate(gddays_post_sow_7d =
           purrr::map_dbl(sowing_date, function(x)
             growing_degree_days(boonah, startdate = x, ndays = 7)),
         stressdays_flower_harvest =
           purrr::map2_dbl(flower_date, harvest_date, function(x, y)
             stress_days_over(boonah, startdate = x, enddate = y)))
print(crop2, n=5)
```

Similarly, to add total rainfall for the 7 days post sowing and the
mean daily radiation from flowering to harvest we use:

```{r, add2crop-totrain}
## Totals and daily means
crop3 <- crop |>
  dplyr::mutate(totalrain_post_sow_7d =
           purrr::map_dbl(sowing_date, function(x)
             cumulative(boonah, var = rain, startdate = x, ndays = 7)),
         meanrad_flower_harvest =
           purrr::map2_dbl(flower_date, harvest_date, function(x, y)
             daily_mean(boonah, var = radn, startdate = x, enddate = y)))
print(crop3, n=5)
```

### Speeding up calculations using `furrr`

For large datasets these calculations can be time consuming. One
approach that may prove useful is to use the `furrr` package which is
a bridge between purrr‘s family of mapping functions and future‘s
parallel processing capabilities. If speed is an issue, then it is
worth trying because it is simple to implement. While some tweaking
may prove useful, it seems that the defaults work pretty well (see
`?future::plan`). After setting the number of workers, then simply
replace mapping functions by putting `future_` at the front of the
name of the mapping function. For instance, `map2_dbl` is replaced
with `future_map2_dbl`. While the results are not shown here, to add
total rain and mean radiation as before, use something like:


```{r, eval=FALSE, add2crop-totrain-furrr}
ptm <- proc.time() # Start the clock!
## set number of 'furrr' workers
library(furrr)
plan(multisession, workers = 2)
## Totals and daily means
crop3 <- crop |>
  dplyr::mutate(totalrain_post_sow_7d =
           future_map_dbl(sowing_date, function(x)
             cumulative(boonah, var = rain, startdate = x, ndays = 7)),
         meanrad_flower_harvest =
           future_map2_dbl(flower_date, harvest_date, function(x, y)
             daily_mean(boonah, var = radn, startdate = x, enddate = y)))
print(crop3, n=5)
proc.time() - ptm # Stop the clock!
```

For recent work, we have found that setting 4 workers was optimal but
this will of course depend on your setup.

