The `boonah` dataset contains meteorological SILO data for the period
1 Jan 2019 to 31 May 2020 obtained from the Longpaddock Queensland
Government DES web site <https://www.longpaddock.qld.gov.au> for
Boonah which is located at -27.9927 S, 152.6906 E. The data is in
`APSIM` format and contains temperature, rainfall, evaporation and
radiation variables and the rows are consecutive days during the
period.  The weather data set was obtained using

```{r get-data, eval=FALSE}
boonah <-
   get_silodata(latitude = "-27.9927", longitude = "152.6906",
                email = "MY_EMAIL_ADDRESS", START = "20190101", FINISH = "20200531")
```

To obtain gridded data, which is what `get_silodata` assumes, you need
to supply at least the site latitude and longitude as well as your
email address by replacing `MY_EMAIL_ADDRESS` with your email
address. The data is freely available under the Creative Commons 4.0
License. Note that SILO may be unavailable between 11am and 1pm
(Brisbane time) each Wednesday and Thursday to allow for essential
system maintenance.

The data obtained is
```{r boonah-data}
## weather data object
print(boonah, n=5)
```
