When modelling crops, agronomists typically specify dates as the day
of year. Several functions are available for day of year calculations
and converting these back to dates. In `R`, dates, times and timezone
data are easily manipulated using the `lubridate` package.

The `day_of_year` function is used to convert a date to the day of
year, which could be based on the calendar year starting on 1 January,
the Australian financial year starting on 1 July or an arbitrary
starting date.

```{r, day-of-year}
##  Day of Calendar Year
day_of_year(ymd(c("2020-12-31", "2020-07-01", "2020-01-01")))
day_of_year(ymd(c("2020-12-31", "2020-07-01", "2020-01-01")), return_year = TRUE)

## Day of Financial Year
day_of_year(ymd(c("2020-12-31", "2020-07-01", "2020-01-01")), type = "financial")
day_of_year(ymd(c("2020-12-31", "2020-07-01", "2020-01-01")), type = "fin",
            return_year = TRUE)
```

To convert a day of year to a date, use `date_from_day_year` noting
that while the calendar year is the default, we can specify the
Australian financial year or an arbitrary starting date.

```{r, date-from-day}
## Convert day of year to a date
date_from_day_year(21,2021)
date_from_day_year(21,2021, type = "fina")
```

Finally, while we can use `day_of_year` to obtain the day of the
current year, if a crop is planted near the end of the year then we
way wish to know the day of harvest which will fall in the next
year. The `day_of_harvest` function provides the day of year in the
year of sowing which can be used to calculate other quantities like
day of flowering etc. Thus, quantities like the number of days between
harvest and sowing are easily calculated taking into account that the
crop may grow past the end of the year. Alternatively, these
quantities are also easily computed directly on the dates by using the
`lubridate` package. For instance the convenience function
`cropgrowdays::number_of_days` is essentially a call to
`as.numeric(finish_date - start_date) + 1`.

```{r, day-of-harvest}
## Day of harvest using the first day of the year of sowing as the base day
day_of_year(ymd("2021-01-05"))
day_of_harvest(x = ymd("2021-01-05"), sowing = ymd("2020-12-20"))  # > 366
```

Note that the first calculation simply assumes the first day of the
year is 1 January 2021 whereas the second calculation yields a result
assuming the first day of the year is 1 January 2020. Hence, since
2020 is a leap year containing 366 days, then the day of harvest is
$366 + 5 = 371$.
