## Quick Start

Install the latest stable version of **cropgrowdays** via CRAN with:
```{r cran-installation, eval = FALSE}
install.packages("cropgrowdays")
```


You can install the development version of **cropgrowdays** from `GitLab` with:
```{r gl-installation, eval = FALSE}
## if you don't have 'remotes' installed, automatically install it
if (!require("remotes")) {
  install.packages("remotes", repos = "http://cran.rstudio.com/")
  library("remotes")
}
install_gitlab("petebaker/cropgrowdays", build_vignettes = TRUE)
```

## Overview

The **cropgrowdays** package provides functions to calculate
agrometeorological quantities of interest for modelling crop
data. Currently, functions are provided for calculating growing degree
days, stress days, cumulative and daily means of weather
data. Australian meteorological data can be obtained from Queensland
Government's Department of Environment and Science (DES) website. In
addition, functions are provided to convert days of the year to dates,
and *vice-versa*.

We recommend using the **cropgrowdays** package in conjunction with
the **tidyverse** and **lubridate** packages.

```{r setup}
suppressMessages(library(tidyverse))
suppressMessages(library(lubridate))
library(cropgrowdays)
```
Note that if you are not familiar with these packages then, in order
to see which functions are provided and which functions conflict with
other packages, initially it may best not to suppress messages using
`suppressMessages`.
